### 2022-03-15 paper/localpsf.tex
restructuring paper

Our method belongs to a class of methods that approximate an operator by interpolating impulse responses of the operator associated with a scattered collection of points. The \emph{impulse response} of $\Aop$ associated with the point $x$ is the function $\impulseresponse_x:\Omega \rightarrow \mathbb{R}$, 
\begin{equation}
\label{eq:impulse_response_defn}
\impulseresponse_x(y) := \Aker(y, x),
\end{equation} 
which results from keeping $x$ fixed and viewing $\Phi(y,x)$ as a function of $y$.
%for a collection of points $x_i$ scattered throughout $\Omega$.
%Further, let $\impulseresponse_x:\Omega \rightarrow \mathbb{R}$,
%\begin{equation}
%\label{eq:impulse_response_defn}
%\impulseresponse_x(y) := \Aker(y, x),
%\end{equation} 
%be the \emph{impulse response} of $\Aop$ at $x$. 
The function $\impulseresponse_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
\impulseresponse_x = \left( \Aop \delta_x^* \right)^*,
\end{equation}
where $\delta_x$ is the the delta distribution (i.e., point source, impulse) centered at $x$, $\Aop \delta_x^* \in L^2(\Omega)'$ is an abuse of notation that denotes the result of applying $\Aop$ to the distribution $\delta_x$, and $\left( \Aop \delta_x^* \right)^* \in L^2(\Omega)$ denotes the Riesz representation of $\Aop \delta_x^*$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\sigma \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\sigma^* \in L^2(\Omega)$ such that $\sigma(v) = \left(\sigma^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} Note that while the domain of $\Aop$ is defined as $L^2(\Omega)$, which does not contain $\delta_x$, if $\Aker$ is sufficiently regular then the action of $\Aop$ may be extended to distributions. This is described in Appendix \ref{app:distributions}.

We assume:
\begin{itemize}
	\item The supports of the impulse responses $\impulseresponse_x$ are contained (or approximately contained) in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all (or nearly all) $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{itemize}
Because of these assumptions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop$ to a small number of polynomial functions. We use the support estimates to compute scattered impulse responses in batches. This batching allows us to recover many impulse responses using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme.

@@

@@

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative integral kernel property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor,
%, let 
%\begin{equation}
%\label{eq:scaled_impulse_response}
%\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
%\end{equation}
%denote the normalized version of $\impulseresponse_x$. 
and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\impulseresponse_x / V(x)), \qquad
\spatialcov(x) := \Var(\impulseresponse_x /V(x)),
\end{equation*}
to be the spatially varying mean and covariance of the normalized version of $\impulseresponse_x$, respectively. Imagine $\phi_x$ as a mound of dirt piled on a localized region in $\Omega$, with $\phi_x(y)$ being the height of the dirt mound at location $y$. The scalar $V(x)$ is the total volume of dirt in the mound, the vector $\mu(x)$ is the center of mass of the dirt mound, and the matrix $\Sigma(x)$ contains information about how wide the dirt mound is in each spatial direction. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$).

@@

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\phi_x(y)/V(x) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) / V(x'). \label{eq:translate4}
%\frac{\phi_x(y)}{V(x)} &\approx \frac{\phi_{x'}\left(y-\mu(x)+\mu(x')\right)}{V(x')}. \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/Nystrom approximation of $\Phi$ \cite{CUR,NYSTROM}.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on \eqref{eq:translate1} computationally expensive. This is the case for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

\subsection{Outline of the method}
\label{sec:intro_overview}

@@

\begin{figure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch1.png}
%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch12.png}
		%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch19.png}
%		\caption{Non-symmetric}
	\end{subfigure}
	\caption{Batches, $\eta_b$, of normalized impulse responses, $\phi_{x_i}/V(x_i)$, for the Stokes Hessian. Left: 2nd batch. Mid: 13th batch. Right: 19th batch. Brightness scale differs between the subfigures. Black stars indicate the sample point locations, $x_i$. Dashed gray ellipses indicate the support ellipsoids, $E_{x_i}$. The large circle is the boundary of the domain $\Omega$. Early batches tend to have lots of ellipsoids near the boundary, as compared to later batches. This is because our greedy ellipsoid packing algorithm tries to pick sample points that are far away from sample points in previously chosen batches.}
	\label{fig:batches_intro}
\end{figure}

@@

\section{Method}
\label{sec:method}
In this section we detail our method for computing the H-matrix approximation, $\mathbf{A}_H$, of $\Aop$, as outlined in Section \ref{sec:intro_overview}.
%The supports of the impulse responses $\phi_x$ are estimated to be contained within ellipsoids (Section \ref{eq:mean_and_covariance_estimation}). The shapes of the ellipsoids depend on spatially varying volume, mean, and covariance functions, $V,\mu,\Sigma$, which we calculate by applying $\Aop$ to a small number of polynomial functions (Section \ref{sec:moments}). We use the ellipsoid support estimates in a greedy ellipsoid packing procedure to choose batches, $\pointbatch_b$, of sample points $x_i$ (Section \ref{sec:sample_point_selection}). Batches, $\eta_b$, of impulse responses, $\phi_{x_i}$, are computed by applying $\Aop$ to Dirac combs associated with the batches of sample points $S_b$. The impulse response batch $\eta_b$ contains the information about all impulse responses $\phi_{x_i}$ associated with points $x_i \in S_b$. Hence, once a small number of impulse response batches $\eta_b$ are computed, they can be used to perform pointwise evaluations $z \mapsto \phi_{x_i}(z)$ for a large number of impulse responses, $\phi_{x_i}$ (Section \ref{sec:get_impulse_response}).
%
%In Section \ref{eq:mean_and_covariance_estimation} we describe our ellipsoid estimate for the support of $\phi_x$. The ellipsoid shape depends on the functions $V,\mu,\Sigma$. We show how to compute these functions in Section \ref{sec:moments}. The ellipsoid support estimates are then used in a greedy ellipsoid packing procedure to choose batches, $\pointbatch_b$, of sample points $x_i$ (Section \ref{sec:sample_point_selection}).
This section is organized as follows:
\begin{description}
	\item[Section \ref{eq:mean_and_covariance_estimation}:] We describe our ellipsoid estimate for the support of $\phi_x$.
	\item[Section \ref{sec:moments}:] We show how to compute $V,\mu,\Sigma$.
	\item[Section \ref{sec:sample_point_selection}:] We present the greedy ellipsoid packing procedure used to choose batches, $\pointbatch_b$, of sample points $x_i$.
	\item[Section \ref{sec:get_impulse_response}:] We describe how to compute $\phi_{x_i}$'s, in batches, $\eta_b$.
	\item[Section \ref{sec:approximate_kernel_entries}:] We show how we interpolate $\phi_{x_i}$'s to approximate $\Phi(y,x)$.
	\item[Section \ref{sec:finite_element_kernel}:] We discuss finite element discretization of $\Phi$.
	\item[Section \ref{sec:h_matrix_construction_short}:] We describe how we construct the H-matrices $\mathbf{\Phi}_H$ and $\mathbf{A}_H$.
	\item[Section \ref{sec:overall_cost}:] We review the total computational cost to construct $\mathbf{A}_H$, and list the cost to perform further linear algebra tasks involving $\mathbf{A}_H$ using H-matrix methods.
\end{description}
The optional method for making $\mathbf{A}_H$ positive semi-definite is described in Appendix \ref{sec:make_spd}. The complete algorithm for constructing $\mathbf{A}_H$ is shown in Algorithm \ref{alg:construct_Atilde}.

@@

\subsection{Impulse response moments}
\label{sec:moments}

%The ellipsoid $E_x$ is not immediately available. 
To determine $E_x$, we must compute the scalar $\spatialvol(x)$, the length-$\gdim$ vector $\spatialmean(x)$, and the $\gdim \times \gdim$ matrix $\spatialcov(x)$.
%(recall $\gdim$ is the spatial dimension of $\Omega$).
The direct approach to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ is to apply $\Aop$ to a point source centered at $x$ to get $\impulseresponse_x$, as per \eqref{eq:impulse_response_delta_action}. Then one can post-process $\impulseresponse_x$ to determine $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$. But this direct approach is computationally infeasible because it requires one operator action of $\Aop$ per point $x$ that we wish to determine $E_x$ at, and we will need to determine $E_x$ at a large number of points. Fortunately, it is possible to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$, \emph{for all points $x\in\Omega$ simultaneously}, by applying $\Aop^T$ to one constant function, $\gdim$ linear functions, and $\gdim(\gdim+1)/2$ quadratic functions. We present this efficient method of computing $\spatialvol$, $\spatialmean$, and $\spatialcov$ in Proposition \ref{thm:vol_mean_cov} and summarize the method for computing these moments in Algorithm \ref{alg:varhpi_mean_cov}.

>>>>

Our method, described in Section \ref{sec:method}, belongs to a class of methods that approximate an operator by interpolating impulse responses of the operator associated with a scattered collection of points. The \emph{impulse response} of $\Aop$ associated with the point $x$ is the function $\impulseresponse_x:\Omega \rightarrow \mathbb{R}$, 
\begin{equation}
\label{eq:impulse_response_defn}
\impulseresponse_x(y) := \Aker(y, x),
\end{equation} 
which results from keeping $x$ fixed and viewing $\Phi(y,x)$ as a function of $y$.
%for a collection of points $x_i$ scattered throughout $\Omega$.
%Further, let $\impulseresponse_x:\Omega \rightarrow \mathbb{R}$,
%\begin{equation}
%\label{eq:impulse_response_defn}
%\impulseresponse_x(y) := \Aker(y, x),
%\end{equation} 
%be the \emph{impulse response} of $\Aop$ at $x$. 
The function $\impulseresponse_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
\impulseresponse_x = \left( \Aop \delta_x^* \right)^*,
\end{equation}
where $\delta_x$ is the the delta distribution (i.e., point source, impulse) centered at $x$, $\Aop \delta_x^* \in L^2(\Omega)'$ is an abuse of notation that denotes the result of applying $\Aop$ to the distribution $\delta_x$, and $\left( \Aop \delta_x^* \right)^* \in L^2(\Omega)$ denotes the Riesz representation of $\Aop \delta_x^*$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\sigma \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\sigma^* \in L^2(\Omega)$ such that $\sigma(v) = \left(\sigma^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} Note that while the domain of $\Aop$ is defined as $L^2(\Omega)$, which does not contain $\delta_x$, if $\Aker$ is sufficiently regular then the action of $\Aop$ may be extended to distributions. This is described in Appendix \ref{app:distributions}.

We assume:
\begin{itemize}
	\item The supports of the impulse responses $\impulseresponse_x$ are contained (or approximately contained) in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all (or nearly all) $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{itemize}
Because of these assumptions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop$ to a small number of polynomial functions. We use the support estimates to compute scattered impulse responses in batches (see Figure \ref{fig:batches_intro}). This batching allows us to recover many impulse responses using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme.

\begin{figure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch1.png}
		%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch12.png}
		%		\caption{Non-symmetric}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\centering
		\includegraphics[scale=0.33]{batch19.png}
		%		\caption{Non-symmetric}
	\end{subfigure}
	\caption{Batches, $\eta_b$, of normalized impulse responses, $\phi_{x_i}/V(x_i)$, for the Stokes inverse problem Hessian. Left: 2nd batch. Mid: 13th batch. Right: 19th batch. Brightness scale differs between the subfigures. Black stars indicate the sample point locations, $x_i$. Dashed gray ellipses indicate the support ellipsoids, $E_{x_i}$. The large circle is the boundary of the domain $\Omega$. Early batches tend to have lots of ellipsoids near the boundary, as compared to later batches. This is because our greedy ellipsoid packing algorithm tries to pick sample points that are far away from sample points in previously chosen batches.}
	\label{fig:batches_intro}
\end{figure}

@@

\section{Preliminaries}

@@

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative integral kernel property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor,
%, let 
%\begin{equation}
%\label{eq:scaled_impulse_response}
%\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
%\end{equation}
%denote the normalized version of $\impulseresponse_x$. 
and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\impulseresponse_x / V(x)), \qquad
\spatialcov(x) := \Var(\impulseresponse_x /V(x)),
\end{equation*}
to be the spatially varying mean and covariance of the normalized version of $\impulseresponse_x$, respectively. Imagine $\phi_x$ as a mound of dirt piled on a localized region in $\Omega$, with $\phi_x(y)$ being the height of the dirt mound at location $y$. The scalar $V(x)$ is the total volume of dirt in the mound, the vector $\mu(x)$ is the center of mass of the dirt mound, and the matrix $\Sigma(x)$ contains information about how wide the dirt mound is in each spatial direction.

%The ellipsoid $E_x$ is not immediately available. 
%(recall $\gdim$ is the spatial dimension of $\Omega$).
The direct approach to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ is to apply $\Aop$ to a point source centered at $x$ to get $\impulseresponse_x$, as per \eqref{eq:impulse_response_delta_action}. Then one can post-process $\impulseresponse_x$ to determine $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$. But this direct approach is computationally infeasible because it requires one operator action of $\Aop$ per point $x$, and we will need to know $V(x)$, $\mu(x)$, and $\Sigma(x)$ at a large number of points $x$. Fortunately, it is possible to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$, \emph{for all points $x\in\Omega$ simultaneously}, by applying $\Aop^T$ to one constant function, $\gdim$ linear functions, and $\gdim(\gdim+1)/2$ quadratic functions. We present this efficient method of computing $\spatialvol$, $\spatialmean$, and $\spatialcov$ in Proposition \ref{thm:vol_mean_cov} and summarize the method for computing these moments in Algorithm \ref{alg:varhpi_mean_cov}.

@@

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\phi_x(y)/V(x) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) / V(x'). \label{eq:translate4}
%\frac{\phi_x(y)}{V(x)} &\approx \frac{\phi_{x'}\left(y-\mu(x)+\mu(x')\right)}{V(x')}. \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/Nystrom approximation \cite{CUR,NYSTROM}.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on \eqref{eq:translate1} computationally expensive. This is the case for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

\section{Method}
\label{sec:method}

@@

@@

In this section we detail our method for computing the H-matrix approximation, $\mathbf{A}_H$, of $\Aop$, as outlined in Section \ref{sec:intro_overview}.
%The supports of the impulse responses $\phi_x$ are estimated to be contained within ellipsoids (Section \ref{eq:mean_and_covariance_estimation}). The shapes of the ellipsoids depend on spatially varying volume, mean, and covariance functions, $V,\mu,\Sigma$, which we calculate by applying $\Aop$ to a small number of polynomial functions (Section \ref{sec:moments}). We use the ellipsoid support estimates in a greedy ellipsoid packing procedure to choose batches, $\pointbatch_b$, of sample points $x_i$ (Section \ref{sec:sample_point_selection}). Batches, $\eta_b$, of impulse responses, $\phi_{x_i}$, are computed by applying $\Aop$ to Dirac combs associated with the batches of sample points $S_b$. The impulse response batch $\eta_b$ contains the information about all impulse responses $\phi_{x_i}$ associated with points $x_i \in S_b$. Hence, once a small number of impulse response batches $\eta_b$ are computed, they can be used to perform pointwise evaluations $z \mapsto \phi_{x_i}(z)$ for a large number of impulse responses, $\phi_{x_i}$ (Section \ref{sec:get_impulse_response}).
%
%In Section \ref{eq:mean_and_covariance_estimation} we describe our ellipsoid estimate for the support of $\phi_x$. The ellipsoid shape depends on the functions $V,\mu,\Sigma$. We show how to compute these functions in Section \ref{sec:moments}. The ellipsoid support estimates are then used in a greedy ellipsoid packing procedure to choose batches, $\pointbatch_b$, of sample points $x_i$ (Section \ref{sec:sample_point_selection}).
This section is organized as follows:
\begin{description}
	\item[Section \ref{eq:mean_and_covariance_estimation}:] We describe our ellipsoid estimate for the support of $\phi_x$.
	\item[Section \ref{sec:moments}:] We show how to compute $V,\mu,\Sigma$.
	\item[Section \ref{sec:sample_point_selection}:] We present the greedy ellipsoid packing procedure used to choose batches, $\pointbatch_b$, of sample points $x_i$.
	\item[Section \ref{sec:get_impulse_response}:] We describe how to compute $\phi_{x_i}$'s, in batches, $\eta_b$.
	\item[Section \ref{sec:approximate_kernel_entries}:] We show how we interpolate $\phi_{x_i}$'s to approximate $\Phi(y,x)$.
	\item[Section \ref{sec:finite_element_kernel}:] We discuss finite element discretization of $\Phi$.
	\item[Section \ref{sec:h_matrix_construction_short}:] We describe how we construct the H-matrices $\mathbf{\Phi}_H$ and $\mathbf{A}_H$.
	\item[Section \ref{sec:overall_cost}:] We review the total computational cost to construct $\mathbf{A}_H$, and list the cost to perform further linear algebra tasks involving $\mathbf{A}_H$ using H-matrix methods.
\end{description}
The optional method for making $\mathbf{A}_H$ positive semi-definite is described in Appendix \ref{sec:make_spd}. The complete algorithm for constructing $\mathbf{A}_H$ is shown in Algorithm \ref{alg:construct_Atilde}.

@@

To determine $E_x$, we must compute the scalar $\spatialvol(x)$, the length-$\gdim$ vector $\spatialmean(x)$, and the $\gdim \times \gdim$ matrix $\spatialcov(x)$. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$).
